NumPy---Array Programming in Python

### 2020-01-26 summary.tex
Fix bibtex

% - 2-3 sentences of basic-level introduction to the field;
Array programming provides powerful notation for accessing,
manipulating, and operating on data in vectors, matrices, and
higher-dimensional arrays \cite{iverson1980notation}.
% - a brief account of the background and rationale of the work;
NumPy is the fundamental array programming library for the Python language
\cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
It has been actively developed for over two decades and has more than 850
contributors, nearly 300,000 dependent repositories on GitHub, and millions of
downloads per year.
%It is one of the most commonly used machine learning tools among
%enterprises \cite{451report2018}.
It plays an essential role in research analysis pipelines in fields as
diverse as physics, biology, astronomy, neuroscience, material science,
engineering, and chemistry.
For example, in astronomy, NumPy was fundamental to discovering gravitational
waves\cite{pycbc}, the first imaging of a black hole\cite{eht-imaging}, and
continues underpinning the future exploration of our
universe\cite{jenness2018lsst}.
% - a statement of the main conclusions (introduced by the phrase 'Here we show' or its equivalent);
Here we show how a few fundamental concepts lead to a simple and
powerful programming paradigm for organizing, exploring, and analyzing
scientific data.
% - 2-3 sentences putting the main findings into general context so it is
%   clear how the results described in the paper have moved the field forwards.
NumPy is the foundation upon which the entire scientific Python
universe is constructed. It is so pervasive that several projects,
targeting audiences with specialized needs, have developed their own
NumPy-like interfaces and array objects.  Because of its central position in the
ecosystem, NumPy increasingly is used to bridge disparate
technologies, opening new possibilities in previously unexplored computational frontiers.

>>>>

% - 2-3 sentences of basic-level introduction to the field;
Array programming provides powerful notation for accessing,
manipulating, and operating on data in vectors, matrices, and
higher-dimensional arrays \cite{iverson1980notation}.
% - a brief account of the background and rationale of the work;
NumPy is the fundamental array programming library for the Python language
\cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
It has been actively developed for over two decades and has more than 850
contributors, nearly 300,000 dependent repositories on GitHub, and millions of
downloads per year.
%It is one of the most commonly used machine learning tools among
%enterprises \cite{451report2018}.
It plays an essential role in research analysis pipelines in fields as
diverse as physics, chemistry, biology, astronomy, geoscience, psychology,
material science, and engineering.
For example, in astronomy, NumPy was fundamental to discovering gravitational
waves\cite{pycbc}, the first imaging of a black hole\cite{eht-imaging}, and
continues underpinning the future exploration of our
universe\cite{jenness2018lsst}.
% - a statement of the main conclusions (introduced by the phrase 'Here we show' or its equivalent);
Here we show how a few fundamental concepts lead to a simple and
powerful programming paradigm for organizing, exploring, and analyzing
scientific data.
% - 2-3 sentences putting the main findings into general context so it is
%   clear how the results described in the paper have moved the field forwards.
NumPy is the foundation upon which the entire scientific Python
universe is constructed. It is so pervasive that several projects,
targeting audiences with specialized needs, have developed their own
NumPy-like interfaces and array objects.  Because of its central position in the
ecosystem, NumPy increasingly is used to bridge disparate
technologies, opening new possibilities in previously unexplored computational frontiers.
